A comparative analysis of penalized linear mixed models in structured genetic data

### 2020-09-24 main.tex
3.5 more wording tweaks

In real data settings CP cannot be calculated since $\bZ \bgamma$ is not directly observed. In simulation settings, however, this ratio is a useful metric for quantifying the degree to which $\bZ \bgamma$ reflects population structure and has the potential to bias SNP-phenotype associations. We will use CP in our interpretation of the simulation results in Section \ref{sec:results}. Given the high-dimensional nature of our data, we approximate $(\bX^\T \bX)^{-1}$ using a low-rank approximation. We use this approach in order to ensure a unique solution.

>>>>

In real data settings CP cannot be calculated since $\bZ \bgamma$ is not directly observed. In simulation settings, however, this ratio is a useful metric for quantifying the degree to which $\bZ \bgamma$ reflects population structure and has the potential to bias SNP-phenotype associations. We will use CP in our interpretation of the simulation results in Section \ref{sec:results}. Given the high-dimensional nature of our data, we use a low-rank approximation of $(\bX^\T \bX)^{-1}$ in order to ensure a unique solution.
